\documentclass[a4paper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=black,pdfnewwindow=true]{hyperref}

\usepackage{fancyhdr}
\usepackage{xurl}
\usepackage{latexsym}
\usepackage{bookmark}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{\item \small{\textbf{#1}:~#2}}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Likhith Aningi}} & \href{mailto:likhithaningi@gmail.com}{likhithaningi@gmail.com} \\
\end{tabular*}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  Hyderabad, India & +91 8639374440 \\
  \multicolumn{2}{l}{
    \href{https://linkedin.com/in/likhith-aningi}{linkedin.com/in/likhith-aningi} \quad
    \href{https://github.com/Likhith-Aningi}{github.com/Likhith-Aningi} \quad
    \href{https://leetcode.com/u/likhithaningi/}{Leetcode} \quad
    \href{https://www.hackerrank.com/profile/n170307/}{HackerRank} \quad
    \href{https://likhith-aningi.github.io/me/}{Portfolio}
    } \\
\end{tabular*}
\vspace{-1em}
\begin{center}
\textit{JAVA DEVELOPER \hfill | \hfill SOFTWARE ENGINEER \hfill | \hfill FULL STACK JAVA ENGINEER}
\end{center}
\vspace{-1em}

\section{Professional Summary}
Full-Stack Java Developer with 2+ years of experience specializing in scalable enterprise applications using Java, Spring Boot, and Microservices. Skilled in designing secure APIs, integrating third-party services, and implementing subscription models leveraging Cashfree, Redis, and MongoDB. Strong expertise in REST/SOAP services, OAuth, CI/CD pipelines, and SQL. Effective both as a collaborative team player and an individual contributor.

\section{Skills Summary}
\resumeSubHeadingListStart
\resumeItem{Languages}{Java, JavaScript, SQL, HTML5, CSS3, Bash}
\resumeItem{Frameworks and libraries}{Spring Boot, React.js, Struts2, Node.js, jQuery}
\resumeItem{Cloud/DevOps}{AWS (S3), Jenkins, Docker}
\resumeItem{Web Services}{REST, JSON, XML, OAuth}
\resumeItem{Databases}{MySQL, MongoDB, Redis, ClickHouse}
\resumeItem{Tools}{Git, Maven, IntelliJ, VS Code, Eclipse, Tomcat, Postman, Swagger}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Way2News Pvt. Ltd.}{Hyderabad, India}{Full Stack Java Developer}{Oct 2022 – Present}
\resumeItemListStart
\item \colorbox{Yellow}{Designed and launched Way2News Gold subscription model} using Spring, Redis, MongoDB, and Cashfree.
\item \textcolor{Green}{Reduced} AWS S3 storage \textcolor{Green}{cost} by 85\% through backend optimization.
\item Developed location-based mapping and analytics for improved user engagement using React.js,Redux,Leaflet,ClickHouse,Spring boot.
\item Integrated secure authentication using MFA with OTPs and device fingerprints.
\item Built REST APIs and third-party service integrations including Twitter, Cashfree, AWS.

\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{IIIT Nuzvid (RGUKT)}{Andhra Pradesh, India}{B.Tech in Computer Science. CGPA: 8.81}{2017 – 2023}
\resumeSubheading{ZPHS Rajapuram}{Andhra Pradesh, India}{SSC. CGPA: 10.0}{2017}
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingListStart
\resumeItem{\colorbox{Green}{Goldman Sachs Engineering Virtual Program}}{\href{https://drive.google.com/file/d/1pOMqlvICYjv8Lg3paqGChd0rFX17uZNx/view?usp=sharing}{Certificate}}
\resumeItem{LinkedIn Learning}{\href{https://drive.google.com/drive/u/1/folders/1enkCm1m-Dm60tNfOQTiLahdnopH1zJEw}{Prompt Engineering, Java, Spring, React courses (Sofar)}}
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeItem{Springboot-JWT-React-Swagger}{Single jar build with JWT auth, Swagger/OpenAPI, React front-end.}
\resumeItem{Employee Registration System}{Java full-stack CRUD app using JSP, Servlets, JDBC, MVC.}
\resumeSubHeadingListEnd

\section{Honors and Achievements}
\resumeSubHeadingListStart
\resumeItem{CRYPTEX Winner}{
  1st Place in Cryptera'21 coding competition – 
  \href{https://www.instagram.com/p/CT4NXFlqCkF/?igsh=ZXhnOXBnb2ZoczE\%3D\&img_index=3}{Link}
}
\resumeItem{Fencing Championship}{Represented RGUKT in All India National Fencing Championship, 2019–20}
\resumeItem{Academic Excellence}{10 GPA in SSC – Felicitated by District Collector}
\resumeSubHeadingListEnd

\end{document}
